---
title: "Group 2- 1st Markdown"
author: "Raphael Lee, Javier Bolong, Tricia Pulmano, Allen Abel"
date: "7/8/2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Personal Answers

1) Aside from the reasons mentioned in class, why do we need to study and analyze data?

- Javier

	Data in essence is information grouped together in the form of statistics and graphs. Being able to analyze what the meaning is behind all of the numbers, means more knowledge in the topic the data pertains too. With this, people can make decisions to adapt to the information given. Without people with the skills in interpreting data correctly, the people who need it will take unguided actions, leading to mistakes and accidents in the future. 
	
2) Cite at least one instance or application where data science was used and contributed on policy-making, day-to-day decisions, knowing market trends, and scientific researches.
  
- Javier 
  
  Data Science was used in helping governments to make proper policies to adapt to the pandemic. One specific instance is lifting certain restrictions of quarantine here in the Philippines. Due to the nature of the virus, the government had to take necessary action to limit human traffic, negatively affecting many businesses which in turn negatively affect the economy. Data/statistics on the state of the pandemic were constantly being updated monthly. With the help of some experts, the government deduced it was time to start allowing non-essential businesses to function to a limited degree.  Without data scientists, the government might have done this in a worse time, worsening the already dire situation of the COVID-19 pandemic. 
  	
3) Propose atleast one data science topic that you want to pursue: Have a broad description of the topic, describe the availability of the data, what kinds of statistical method you think you will need, and who would benefit this study.
  	
- Javier 
  		
  In the modern world, data mining is essential knowledge. We are in an age where information is large in quantity and widespread throughout the known world. To process this amount of data is what data mining does. In order to organize the entire procedure, I think graphs like histograms are needed. This is an incredible venture and requires clear models to make correct conclusions. However, there is still much data/research for this particular field, which can help me in learning whatever needs to be known about it. Large companies will most likely benefit from this study.  They are often associated with a large amount of clientele and assets. There will be a huge amount of information that comes from this and there will be a demand for experts to sort this through.


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Why do we need to study and analyze data? (Abel)

- Data when analysed and used can influenced a lot of things from a regular person everyday activities to that of a country's economy and government

- It can help the person improve their analytical skills which can be useful in some field

- Solution to a problem can originate from a unconventional or not expected way

- It can be used to backup or disprove arguments

- Make Informed Decisions

- Optimizations


## One instance or application where data science was used.

It can be used in business where it can help the company save money. An example of this is the Network Planning Tool that UPS use to optimize package transport from drop-off to delivery. It does this by using machine learning and AI to simulate a variety of routes and picks the best ones. According to a company forecast, the platform could save UPS 100 to 200 million.

Not only it can be use to save money, companies can also used it to be able to have the maximum profit. This is most prevalent online where a lot of data and statistics are used to determine what kind of advertisment that will be shown and how to retain the most amount of time

Another field in which it can be used is in sports. One of this is RSPCT: BASKETBALL-COACHING SENSOR. RSPCT’s shooting analysis system tracked and record when and where the ball strikes on each basket attempt by using sensor on a basketball hoop’s rim. It funnels that data to a device that displays shot details in real time and generates predictive insights.

Lastly it can be used by the goverment to help secure the country. This example was done in the USA wherein 
the U.S. Immigrations and Customs Enforcement uses facial recognition to deport undocumented immigrants


## Proposal

    A chatbot is a software application used to conduct an online chat conversation via text or text-to-speech instead of a human. I chose this because of how prevalent chatbots arein todays society and how customizable it is. It can be used to help us in alot of things like automating tasks, act as a communication medium and to even use as a mean to play games. 

Since a chatbot is very customizable to whatever the programmer's goal, there are many kinds data that can be used into making the bot. Even if there are not that many data available, the more people uses and input information into the bot it itself can be the source of data into which it can improve on. Some of the statistical method that can be use are surveys which can be use to improve the bot, cluster sampling and Sample Size Determination to have a data on which the bot will be exposed to and Regression to determining trends over time, connections that which will help the bot not be outdated and up to date with whats happening with the world.
